Financialisation of Commodity Markets

### 2024-10-30 docs/paper.qmd
Include regime difference test results table

>>>>

```{r}
#| label: tbl-regime-diference-tests
#| tbl-cap: "This table shows the results for tests of difference in mean (t-test) and variance (F-test) between phases of aggregate backwardation and contango for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). 1%, 5% and 10% p-value levels are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively in the significance column. Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."

colnames <- c("asset", "period", "moment", "dominant regime", "p-value", "significance")
align <- make_series_of_repeated_chars(list(l = 4L, r = 2L))

make_table("regime difference tests", colnames, align, 1L:4L, 5L:6L)
```
